---
title: "ETC5521 Assignment 1"
subtitle: "Analysis of global mobile and fixed telephone usage"
team: brolga
author:
  - Hanchen Wang 
  - Jiaying Zhang 
date: "`r Sys.Date()`"
output: 
  html_document
bibliography: reference.bib
---

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")
library(dplyr)
library(readr)
library(tidyverse)
library(here)
```

```{r rawData, include = FALSE}
mobile <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-10/mobile.csv')
landline <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-10/landline.csv')
```
# Introduction and motivation

It has been 45 years since the first landline telephone was invented in 1876. The telephone has changed a lot from how it works to how it looks. Today, mobile technology has spread rapidly around the globe and it is estimated that more than 5 billion people have mobile devices, and over half of these connections are smartphones. 

“Digital connectivity plays a critical role in bettering lives, as it opens the door to unprecedented knowledge, employment and financial opportunities for billions of people worldwide,” said ITU Secretary-General Houlin Zhao. Because the telephone plays a crucial role in our life, we think it is valuable to analyze it.

This analysis is based on information about mobile and landline phones collected by the @ITU -International Telecommunication Union and would like to analyze the phone subscription trend, percentage and other factors.

Specially: 

1.What is the trend in subscription of phone and landline worldwide between 1990 and 2017?

2.What is the difference and occupation between phone and landline subscriptions in different countries in given year?

3.What is the regression relationship between phone subscriptions and other variables? 

# Data description

The datasets are downloaded from the Github repository of [Tidy Tuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-11-10). @Tidy-Tuesday is a weekly data project aimed at the R ecosystem and this report will use datasets adopted by it on November 10, 2020.

There are two datasets provided in the repository and all of them came from an article-"Technology Adoption" which written by @owidtechnologyadoption on 2017 [OurWorldInData.org](https://ourworldindata.org/technology-adoption). 

## Mobilephone subscriptions vs GDP per capita  (`mobile.csv`)
The dataset about Mobilephone subscriptions vs GDP per capita originated from an article-"Technology Adoption". This dataset was published by [@Worldbank – World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) and collected by [@ITU - International Telecommunication Union](https://www.itu.int/en/ITU-D/Statistics/Pages/publications/wtid.aspx). The dataset cover the data about mobilephone subscriptions and GPD per capita in each country from 1960 to 2017.


Mobile cellular telephone subscriptions are subscriptions to a public mobile telephone service that provide access to the PSTN using cellular technology. The indicator includes (and is split into) the number of postpaid subscriptions, and the number of active prepaid accounts (i.e. that have been used during the last three months). The indicator applies to all mobile cellular subscriptions that offer voice communications. It excludes subscriptions via data cards or USB modems, subscriptions to public mobile data services, private trunked mobile radio, telepoint, radio paging and telemetry services.

Data on mobile cellular subscribers are derived using administrative data that countries (usually the regulatory telecommunication authority or the Ministry in charge of telecommunications) regularly, and at least annually, collect from telecommunications operators.

Data for this indicator are readily available for approximately 90 percent of countries, either through ITU's World Telecommunication Indicators questionnaires or from official information available on the Ministry or Regulator's website. For the rest, information can be aggregated through operators' data (mainly through annual reports) and complemented by market research reports.

This dataset has `r nrow(mobile)` number of observations and `r ncol(mobile)` number of variables. The name, type and description of each variable in `mobile.csv` can be found in the data dictionary below.



|variable          |class     |description |
|:-----------------|:---------|:-----------|
|entity            |character | Country |
|code              |character | Country code |
|year              |double    | Year |
|total_pop         |double    | Gapminder total population |
|gdp_per_cap       |double    | GDP per capita, PPP (constant 2011 international $) |
|mobile_subs       |double    | Fixed mobile subscriptions (per 100 people) |
|continent         |character | Continent |


## Fixed(landline) telephone subscriptions vs GDP per capita  (`landline.csv`)

The dataset about Fixed(landline) telephone subscriptions vs GDP per capita also originated from "Technology Adoption". It published by [@Worldbank – World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) and collected by [@ITU - International Telecommunication Union](https://www.itu.int/en/ITU-D/Statistics/Pages/publications/wtid.aspx). The dataset cover the data about fixed telephone subscriptions and GPD per capita in each country during 1960 and 2017.

Fixed telephone subscriptions refers to the sum of active number of analogue fixed telephone lines, voice-over-IP (VoIP) subscriptions, fixed wireless local loop (WLL) subscriptions, ISDN voice-channel equivalents and fixed public payphones.

Data on fixed telephone lines are derived using administrative data that countries (usually the regulatory telecommunication authority or the Ministry in charge of telecommunications) regularly, and at least annually, collect from telecommunications operators. 

Data for this indicator are readily available for approximately 90 percent of countries, either through ITU's World Telecommunication Indicators questionnaires or from official information available on the Ministry or Regulator's website. For the rest, information can be aggregated through operators' data (mainly through annual reports) and complemented by market research reports.

This dataset has `r nrow(landline)` number of observations and `r ncol(landline)` number of variables. The name, type and description of each variable in `landline.csv` can be found in the data dictionary below.

|variable                           |class     |description |
|:----------------------------------|:---------|:-----------|
|entity                             |character |Country         |
|code                               |character | Country code |
|year                               |double    | Year |
|total_pop |double    | Gapminder total population |
|gdp_per_cap                        |double    | GDP per capita, PPP (constant 2011 international $) |
|landline_subs                      |double    | Fixed telephone subscriptions (per 100 people)|
|continent                          |character | Continent |

# Analysis and findings

[FILL] Should include at least one plot or numerical summary for each of your questions, that helps the reader arrive at an answer. You should also write paragraphs describing the methods, summaries and findings. 

# References
